### 2017-10-10 character_coding/CharacterEvolution.Rmd
changed index column sequence for depth physignal

```{r phylosig_depth_declare, message=F, warning=F, include=FALSE}
depth_physig = physignal(dpruned_data[,c(13,14,15,17,18)], dpruned_tree)
depth_multisig = multiPhylosignal(dpruned_data[,c(13,14,15,17,18)], dpruned_tree)
```
###Phylogenetic signal in VARS bathymetrics
```{r phylosig_depth, echo=F, message=F, warning=F}
depth_physig
depth_multisig
```

>>>>

```{r phylosig_depth_declare, message=F, warning=F, include=FALSE}
depth_physig = physignal(dpruned_data[,c(14,15,16,18,19)], dpruned_tree)
depth_multisig = multiPhylosignal(dpruned_data[,c(14,15,16,18,19)], dpruned_tree)
```
###Phylogenetic signal in VARS bathymetrics
```{r phylosig_depth, echo=F, message=F, warning=F}
depth_physig
depth_multisig
```

### 2017-10-10 manuscript.rmd
changed index column sequence for depth physignal

```{r phylosig_depth_declare, message=F, warning=F, include=FALSE}
depth_physig = physignal(dpruned_data[,c(13,14,15,17,18)], dpruned_tree)
depth_multisig = multiPhylosignal(dpruned_data[,c(13,14,15,17,18)], dpruned_tree)
```
Phylogenetic signal in VARS bathymetrics
```{r phylosig_depth, echo=F, message=F, warning=F}
depth_physig
depth_multisig
```

>>>>

```{r phylosig_depth_declare, message=F, warning=F, include=FALSE}
depth_physig = physignal(dpruned_data[,c(14,15,16,18,19)], dpruned_tree)
depth_multisig = multiPhylosignal(dpruned_data[,c(14,15,16,18,19)], dpruned_tree)
```
Phylogenetic signal in VARS bathymetrics
```{r phylosig_depth, echo=F, message=F, warning=F}
depth_physig
depth_multisig
```
